$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added comment explaining smaller scans were used to fill in the general U(1)' model plots

\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cc}
MSSM & E$_6$SSM \\
\hline
$2 \leq \tan\beta \leq 50$& $2 \leq \tan\beta \leq 50$ \\
$-1\textrm{ TeV } \leq \mu \leq 1 \textrm{ TeV}$ & $-3 \leq \lambda \leq 3$\\
$-1\textrm{ TeV } \leq B \leq 1\textrm{ TeV}$ & $-10\textrm{ TeV } \leq A_\lambda \leq 10\textrm{ TeV}$ \\
$ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$\\
$ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$\\
$ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ & $ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$\\
$M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ & $M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ \\
\end{tabular}
\end{ruledtabular}
\caption{The parameters scanned over and the ranges of values used in
  the MSSM and the $E_6SSM$ models.}
\label{tab:scanranges}
\end{table}

@@

The exact level of tuning from the $Z^\prime$ depends on the charges
of the extra $U(1)$ gauge symmetry it is associated with.  In
Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine tuning for
other U(1) extensions for the same $Z^\prime$ masses as we did for the
E$_6$SSM.  To simplify the analysis we fix $\tan \beta = 10$, but scan
over the remaining parameters as in Table \ref{tab:scanranges} and fix
the rest to the same values we did in the scan carried out for
Fig.~\ref{Fig:e6ssmvsmssm}.

>>>>

\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cc}
MSSM & E$_6$SSM \\
\hline
$2 \leq \tan\beta \leq 50$& $2 \leq \tan\beta \leq 50$ \\
$-1\textrm{ TeV } \leq \mu \leq 1 \textrm{ TeV}$ & $-3 \leq \lambda \leq 3$\\
$-1\textrm{ TeV } \leq B \leq 1\textrm{ TeV}$ & $-10\textrm{ TeV } \leq A_\lambda \leq 10\textrm{ TeV}$ \\
$ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{Q_3} \leq 2000 \textrm { GeV}$\\
$ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$ & $ 200 \textrm{ GeV } \leq m_{u_3} \leq 2000 \textrm { GeV}$\\
$ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$ & $ -10 \textrm{ TeV } \leq A_t \leq 10 \textrm { TeV}$\\
$M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ & $M_2=100\textrm{ GeV, } 1050\textrm{ GeV, } 2000 \textrm{ GeV}$ \\
\end{tabular}
\end{ruledtabular}
\caption{The parameters scanned over and the ranges of values used in
  the MSSM and the E$_6SSM$ models.}
\label{tab:scanranges}
\end{table}

@@

The exact level of tuning from the $Z^\prime$ depends on the charges
of the extra $U(1)$ gauge symmetry it is associated with.  In
Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine tuning for
other U(1) extensions for the same $Z^\prime$ masses as we did for the
E$_6$SSM.  To simplify the analysis we fix $\tan \beta = 10$, but scan
over the remaining parameters as in Table \ref{tab:scanranges} and fix
the rest to the same values we did in the scan carried out for
Fig.~\ref{Fig:e6ssmvsmssm}. In order to more clearly identify the lower bound
on the obtainable tuning in each model, the parameter values for points in
these main grid scans with a low fine tuning were then used as the starting points for
smaller scans about those values. In these smaller scans the parameters were more finely
varied to populate the low fine tuning regions.
